### 2014-11-11 tex/intro.tex
made a pass on the intro; still needs work

In recent years symbolic execution --
a program analysis technique for systematic exploration of
program execution paths using symbolic input values -- has provided
the basis for many software testing and analysis techniques.
For each execution path explored during symbolic execution, constraints
on the symbolic inputs are collected to create a \emph{path
condition}. The set of path conditions computed by symbolic execution
characterize the observed program execution behaviours and can
be used to perform various analyses of program behavior, e.g.,
regression testing~\cite{} and differential program 
analysis~\cite{}.

Initial work on symbolic execution largely focused on checking 
properties of programs with primitive types, such as integers and 
booleans~\cite{clarke76TSE,King:76}. With the advent of object-oriented
languages, such as Java and C$++$, one of the fundamental challenges 
of using symbolic execution for program analysis
has been how to analyze programs containing
complex data structures with unbounded domains, i.e., data stored
on the heap. State-of-the-art symbolic execution techniques have 
addressed this challenge by constructing the heap in a lazy manner, 
deferring materialization of objects on the concrete heap until
they are needed, i.e., until execution of a statement with a 
dereference expression ($x = r.f$)~\cite{Kiasan06,Kiasan07,GSE03}.

Although the lazy symbolic execution techniques have been instrumental 
in enabling analysis of heap manipulating software, treatment of
heap data follows concrete program semantics once a heap location is
materialized. The effect is to exacerbate 
the state space explosion problem by creating additional points of 
non-determinism during symbolic execution to account for the 
different possible concrete heap configurations.

Need a transition here to talk about a symbolic heap

In this paper we present a novel approach to lazy symbolic
execution....

Our technique is 1) scalable -- it constructs the symbolic
heap on-the-fly during symbolic execution but avoids introducing 
additional points of non-determinism
by maintaining only a (fully) symbolic heap,
2) precise -- at any given point during symbolic execution, 
the symbolic heap represents the exact set of feasible
concrete heap structures for the program under analysis, and
3) expressive -- the symbolic heap can represent recursive data structures 
and heaps resulting from loops and recursive control structures in the code. 
We report on a case-study of an implementation of our technique in the
Symbolic PathFinder tool to illustrate
 its scalability and we discuss how test case generation -- a common
 use for the results of symbolic execution -- can benefit from symbolic
 execution using a fully symbolic heap.

This paper makes the following contributions:

\begin{itemize}
\item{We present a novel technique for analyzing heap manipulating
programs that constructs a fully symbolic representatino of
the heap on-the-fly durig symbolic execution.}
\item{We prove the soundness and completeness of our algorithm...}
\item{We implement our approach in the Symbolic PathFinder tool}
\item{We demonstrate experimentally that our technique improves
the scalability of symbolic execution of heap maninpulating software
over state-of-the-art techniques.}

 \end{itemize}

>>>>

In recent years symbolic execution has provided the basis for various 
software testing and analysis techniques. Symbolic execution
systematically explores the program execution space using
symbolic input values, and for each explored path, computes
constraints on the symbolic inputs to create a \emph{ path condition}.
The set of path conditions computed by
symbolic execution characterize the observed program execution
behaviours and have been used as an enabling technology for various
applications, e.g., regression
analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
data structure repair~\cite{KhurshidETAL05RepairingStructurally},
dynamic discovery of
invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
debugging~\cite{Ma:2011}.

Initial work on symbolic execution largely focused on checking 
properties of programs with primitive types~\cite{clarke76TSE,King:76}.
%, e.g., integers and booleans 
%Despite recent advances
%in constraint solving technologies, improvements in
%raw computing power, and advances in reduction
%and abstraction techniques~\cite{AnandETAL2009AbsSymExe,Godefroid:POPL07}
%symbolic execution of programs of modest size containing only
%primitive types, remains challenging
%because of the large number of execution paths generated
%during symbolic analysis. 
With the advent of object-oriented languages,
% e.g., Java and C$++$, 
recent work has generalized the core ideas of symbolic execution to enable 
analysis of programs containing complex data structures with unbounded 
domains, i.e., data stored on the heap~\cite{Kiasan06,Kiasan07,GSE03}.  
These Generalized Symbolic Execution (GSE) techniques construct the 
heap in a lazy manner, deferring
materialization of objects on the concrete heap until they are needed
for the analysis to proceed. The materilization 
%accounts for various heap configurations, 
creates additional non-deterministic 
choice points in the symbolic execution tree representing 
the feasible heap configurations.
as (a) null, (b) instance of a new
reference of a compatible class, and (c) alias an previously
initialized symbolic reference. 
Symbolic execution follows concrete program semantics for 
materialized heap locations. Although this approach
enables analysis of heap manipulating programs, a large number
of feasible concrete heap configurations may be created 
exacerbating
the well known state space explosion problem
associated with symbolic execution.

%  resulting in a large number of feasible concrete heap
%configurations, and as a result, a large number of points of
%non-determinism to be analyzed.
%, further exacerbating the state space
%explosion problem.

Research in the abstract interpretation community has taken
a very different approach to analyzing heap manipulating
programs which computes a summary of possible heaps. 
These techniques start with an initial heap configuration 
and then using a static analysis, make updates to the
heap following program semantics, ultimately creating a heap 
summary which represents the potential heaps resulting from
program execution~\cite{Dillig:2011}. Because these
techniques are based on a static analysis, the heap summaries
over-approximate the set of feasible heap configurations.
%The primary challenge relative to heap
%analysis for these techniques is to 
%resolve potential dependencies of local results on the global
%aliases in the heap. 
%Recent work addresses these issues
%through strong updates to heap locations 
%at call sites~\cite{Dillig} and computation of dangerous 
%aliases~\cite{Matosevic}. Because these techniques are based 
%on a static analysis, the resulting summaries over-approximate
%the actual potential heaps.

In this work, we present a novel heap initialization and analysis 
technique which takes inspiration from both GSE and existing
heap summarization techniques. The intuition behind our analysis
is to construct the heap lazily during symbolic execution
but reduce the points of non-determinism in
the symbolic execution tree by analyzing each control-flow
path only once for any given set of isomorphic heaps. To 
represent the exact set of feasible concrete heap structures 
resulting from execution of the control-flow path, we use
a heap summary.
Our analysis improves on existing GSE approaches by 
reducing the size of the symbolic execution state space explored,
thereby improving scalability of symboic execution for heap
manipulating software. It improves on existing heap summarization
techniques by enabling analysis of arbitrary recursive data structures 
(no initial heap configuration is required) while avoiding the imprecision
introduced by these techniques.

\nsr{a paragraph that provides a breif summary
  of the results.. would be nice if we have numbers for lazier and
  lazier Sharp as well.}
  A preliminary evaluation of our technique
shows that it can improve the scalability of symbolic execution
of heap manipulating programs X fold over GSE-based analyses
while maintaining precision and efficiency.

This paper makes the following contributions:
\begin{itemize}
\item{We present a novel inter-procedural analysis technique for 
symbolic execution of heap manipulating software which constructs 
a precise heap summary.}
\item{We use the JavaLite language~\cite{saints-MS} to formalize 
the algorithm for constructing and manipulating the heap summary
on-the-fly during symbolic execution.}
\item{We implement our approach in the Symbolic PathFinder tool and
empirically demonstrate that our technique improves
the scalability of symbolic execution of heap maninpulating software
over GSE, while maintaining efficiency and precision.}
\item{We prove that at any given point during symbolic execution, the symbolic 
heap represents the exact set of feasible concrete heap structures 
for the program under analysis.}
 \end{itemize}

%\nsr{needs
%  some text on the fact we use java lite to formalize the heap
%  summary, some key characteristicss of the heap such as the fact it
%  is a bipartiate graph with locations and referneces, properties of
%  the heap such as the determinism and immutability}
\nsr{Is any part of the formalism borrowed
from the dilligs? Which part are unique?}  \nsr{end on a couple
sentences about the various rules that will be talked about in the
paper}

\nsr{The reader should be convinced about our expressiveness
  claim here}

\nsr{a paragraph that provides intution on how we are a bisumulation
  with the GSE..reader should be convinced about the precision claim}
